%%% Kieran's Vita. Full.
%%% /Users/kjhealy/projects/vita/vita.tex


\documentclass[11pt]{article}
  
%% Git version tracking
\input{vc}

%% misc style files
\usepackage{url,fancyhdr,revnum}

%% needed for xelatex to work
\usepackage{fontspec}
\usepackage{xunicode}

%% color 
\usepackage[usenames,dvipsnames]{color}

%% meta
\def\myauthor{Kieran Healy}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{Duke University}
\def\myaddress{Sociology Department}
\def\myemail{kjhealy@soc.duke.edu}
\def\myweb{http://www.kieranhealy.org}
\def\myphone{}
\def\myversion{}
\def\myrevision{}


\def\myaffiliation{Duke University}
\def\myauthor{Kieran Healy}
\date{2008-09-10}
\def\mykeywords{Kieran, Healy, Kieran Healy, Vita, CV, Resume, Sociology}

%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	urlcolor=BlueViolet,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

\begin{document}

%% Choose fonts
\setromanfont[Mapping={tex-text},Numbers={OldStyle},Ligatures={Common}]{Minion Pro} 
\setsansfont[Mapping=tex-text,Colour=AA0000]{Myriad Pro}
\setmonofont[Mapping=tex-text,Scale=0.9]{Pragmata} 

%% custom ampersand
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%% page layout
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyfoot{}
\rhead{{\scriptsize\thepage}}
\rfoot{\texttt{\scriptsize \VCRevision\ on \VCDateTEX}} % git revision info inserted via external script -- see docs for vc package for details. comment out this line if you're not using vc.

%% address and contact block
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize \href{http://www.soc.duke.edu}{Department of Sociology} \\ Box 90088, \\ Duke University, \\ \vspace{-0.05in} Durham, \textsc{nc} 27708}  
  
\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize Phone: (650) 321-2052 \\ 
  Fax: (650) 321-1192  \\ 
  {\scriptsize  \texttt{\href{mailto:kjhealy@soc.duke.edu}{kjhealy@soc.duke.edu}}} \\
  {\scriptsize  \texttt{\href{http://www.kieranhealy.org}{http://www.kieranhealy.org}}}
\end{minipage}


\medskip

%% Name 
\noindent{\Large {\textsc{kieran healy}}}
\reversemarginpar

\medskip       

%% Appointments
\medskip
\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright Appointments}}}

\noindent\emph{Duke University \vspace{0.01in}}

\ind 2009--Present. Associate Professor in Sociology and the Kenan Institute for Ethics.      

\ind 2008--2009. Visiting Associate Professor of Sociology.

\medskip
\noindent\emph{University of Arizona \vspace{0.01in}}

\ind 2008. Associate Professor of Sociology.

\ind 2001--2008. Assistant Professor of Sociology.

\medskip

\noindent\emph{Australian National University \vspace{0.01in}}

\ind 2003--2006. Research Fellow, Social and Political Theory Program,
Research School of Social Sciences.

\bigskip

%% Education

\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright Education}}}

\noindent\emph{Princeton University \vspace{0.01in}}

\ind 2001. Ph.D, Sociology. % Dissertation: \emph{Exchange in Blood and
%   Organs}. %\vspace{-0.1in}  

% \begin{itemize}
% 	\item \small Winner of the American Sociological Association's Dissertation
% 	  Award for 2002.
% \end{itemize}      


\ind 1998. M.A., Sociology. (General Examinations with Distinction.)


\medskip
\noindent\emph{National University of Ireland (Cork)\vspace{0.02in}}

\ind 1994. M.A., Sociology. (First Class Honors.) \vspace{0.01in}


\ind 1993. B.A., Sociology and Geography. (Joint First Class Honors.) 

\bigskip
 
%% Publications
\marginpar{\textsf{{\footnotesize\vspace{-0.7em}\flushright Publications}}}
\medskip
\noindent\emph{Book \vspace{0.01in}}

\ind  Kieran Healy. 2006. \emph{\href{http://www.lastbestgifts.com}{Last Best Gifts: Altruism and the Market for Human Blood and Organs}}. Chicago:~University of Chicago Press. \vspace{-0.075in}

% \begin{itemize} 
% 	\item \small Honorable Mention, American Sociological Association Section on Economic Sociology, Zelizer Distinguished Scholarship Award, 2008.
% 	\item \small Winner, Association for Research on Nonprofit Organizations and Voluntary Action, Outstanding Book Award, 2007.
% 	\item \small Finalist, Society for the Study of Social Problems, C. Wright Mills Award, 2006.  
% 	% \item \small Reviews: \href{http://www.journals.uchicago.edu/doi/pdf/10.1086/522391}{\emph{American Journal of Sociology}} (Greta Krippner), \href{http://www.kieranhealy.org/files/misc/hippenajot.pdf}{\emph{American Journal of Transplantation}} (Ben Hippen), \emph{Social Forces} (Jane Allyn Piliavin),    \href{http://www.nytimes.com/2007/01/28/books/review/Postrel.t.html?ex=157680000&en=f390b3396e0ec28a&ei=5124&partner=permalink&exprod=permalink}{\emph{The New York Times}} (Virginia Postrel), \href{http://nvs.sagepub.com/cgi/rapidpdf/0899764008319689v1}{\emph{Nonprofit and Voluntary Sector Quarterly}} (E. Gil Clary), \href{http://ser.oxfordjournals.org/cgi/reprint/6/2/365}{\emph{Socio-Economic Review}} (Philippe Steiner), \emph{Le Mouvement Social} (Sophie Chauveau), \href{http://www.australianreview.net/digest/2007/06/waldby.html}{\emph{Australian Review of Public Affairs}} (Catherine Waldby), \href{http://econsoc.mpifg.de/archive/econ_soc_08-1.pdf}{\emph{EES Newsletter}} (Rene Almeling),  \href{http://www.anthrosource.net/doi/pdfplus/10.1111/j.1548-1387.2008.00006_3.x}{\emph{Medical Anthropology Quarterly}} (Lesley Sharp), \href{http://www.sciencedirect.com/science?_ob=ArticleURL&_udi=B6VR1-4RTCPT9-B&_user=56761&_coverDate=03%2F31%2F2008&_alid=760447016&_rdoc=1&_fmt=high&_orig=search&_cdi=6221&_sort=d&_docanchor=&view=c&_ct=1&_acct=C000059541&_version=1&_urlVersion=0&_userid=56761&md5=4e61d07203022b07cbdc0d671747f7b3}{\emph{Sociologie du Travail}} (Philippe Steiner).          
% \end{itemize}     

\normalsize

\bigskip
\noindent\emph{Journal articles \vspace{0.05in}}
 
%% Use revnumerate environment if numbered publications are needed.
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

\ind Marion Fourcade and Kieran Healy. 2007. ``\href{http://arjournals.annualreviews.org/doi/pdf/10.1146/annurev.soc.33.040406.131642}{Moral Views of Market Society}.'' \emph{Annual Review of Sociology} 33:~285--311. 

\ind Kieran Healy. 2006. ``\href{http://www.kieranhealy.org/files/papers/presumed-consent.pdf}{Do Presumed Consent Laws Raise Organ Procurement Rates?}'' \emph{DePaul Law Review} 55:~1017--1043. 

\ind Kieran Healy. 2004. ``\href{http://www.kieranhealy.org/files/papers/asr2004.pdf}{Altruism as an Organizational Problem: The Case of Organ Procurement}.''
 \emph{American Sociological Review} 69:~387--404.

\ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/jpp.pdf}{Digital Technology and Cultural Goods}.'' \emph{Journal of
  Political Philosophy} 10:~478--500. 

\ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/culture-newecon.pdf}{What's New for Culture in the New Economy?}'' \emph{Journal
  of Arts Management, Law and Society} 32:~86--103. 


\ind Kieran Healy. 2000. ``\href{http://www.kieranhealy.org/files/papers/embed-alt.pdf}{Embedded Altruism: Blood Collection Regimes and the European
  Union's Donor Population}.'' \emph{American Journal of Sociology} 105:~1633--\,1657.


\ind Kieran Healy. 1999.  ``\href{http://www.kieranhealy.org/files/papers/ts.pdf}{The Emergence of \textsc{hiv} in the U.S. Blood Supply: Organizations,
  Obligations and the Management of Uncertainty}.'' \emph{Theory and Society} 28:~529--558.


\ind Bruce Western and Kieran Healy. 1999. ``\href{http://www.kieranhealy.org/files/papers/western-healy99.pdf}{Explaining the OECD Wage Slowdown:
Recession or Labor Decline?}''  \emph{European Sociological Review}
15:~233--249.


\ind  Kieran Healy. 1998.  ``\href{http://www.kieranhealy.org/files/papers/constraint98.pdf}{Conceptualising Constraint: Mouzelis, Archer and the concept of
  social structure}.'' \emph{Sociology} 32:~509--522. 

%\end{revnumerate}
%\newpage
\bigskip

\noindent\emph{Book chapters \vspace{0.05in}}
% \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
% \begin{revnumerate}

\ind Kieran Healy. Forthcoming. ``Social Structure, Gifts and Norms in \emph{The Story of Qiu Ju},'' in \emph{Norms and Values: The Role of Social Norms as Instruments of Value Realisation}, edited by Michael Baurmann, Geoffrey Brennan, Robert E. Goodin and Nicholas Southwood. Baden Baden: Nomos Verlag.

\ind Kieran Healy. 2008. ``Lo Scambio di Doni,'' in \emph{L'Altro in Me: Dono del Sangue fra Culture, Pratiche e Identità}, edited by Annamaria Fantauzzi. Milano: \textsc{avis} Nazionale, 36--42. 

\ind Kieran Healy. 2007. ``Sociology,'' in \emph{A Companion to Contemporary Political Philosophy} (Second Edition), edited by Robert E. Goodin, Philip Pettit and Thomas Pogge. New York: Blackwell, 90--122. 

\ind  Kieran Healy. 2004. ``Sacred Markets and Secular Ritual in the Organ Transplant
Industry,'' in \emph{The Sociology of the Economy}, edited by Frank Dobbin. New
York: Russell Sage, 336--359.

\ind Bruce Western and Kieran Healy.  2001.  ``Wage Growth and Labor Decline in the
Industrialized Democracies, 1965--1993,'' in \emph{Unemployment in the New
  Europe}, edited by Nancy Bermeo. New York: Cambridge University Press,
121--144.

 \ind  Kieran Healy. 1998. ``The New Institutionalism and Irish Social Policy,'' in
\emph{Social Policy in Ireland: Principles, Practice and Problems}, edited by
Se\'{a}n Healy and Brigid Reynolds. Dublin: Oak Tree Press, 59--83.

%\end{revnumerate}

\bigskip 
 
%\newpage
\noindent\emph{Reviews and other occasional writing \vspace{0.05in}}

%\renewcommand{\labelenumi}{\textsc{r}\theenumi.}
%\begin{revnumerate}
\ind Kieran Healy. 2009. \href{http://www.journals.uchicago.edu/doi/pdf/10.1086/605757}{Review} of \emph{Pop Finance} by Brooke Harrington. \emph{American Journal of Sociology} 115:~309--12.

\ind Kieran Healy. 2007. ``\href{http://www.kieranhealy.org/files/reviews/socforum-article.pdf}{A Wealth of Notions}.'' Review
Essay on \emph{Freakonomics} by Steven Levitt and Stephen Dubner. \emph{Sociological Forum} 22:~119--125. 

\ind  Kieran Healy. 2006. ``Sacred.'' In \emph{International Encyclopedia of Economic Sociology}, edited by Jens Beckert and Milan Zafirovski. London: Routledge, 588--589. 

\ind  Kieran Healy. 2005. \href{http://www.kieranhealy.org/files/reviews/klinenberg.pdf}{Review} of \emph{Heat Wave} by Eric Klinenberg. \emph{Imprints} 8:~283--289.

\ind  Kieran Healy. 2005. \href{http://www.kieranhealy.org/files/reviews/fox.pdf}{Review} of \emph{An R and S-PLUS Companion to Applied Regression}, by John Fox. \emph{Sociological Methods and Research} 34:~137--140.

\ind  Kieran Healy. 2005. ``\href{http://www.kieranhealy.org/files/reviews/henwood.pdf}{After the Ball was Over}.'' Review of \emph{After the New
  Economy} by Doug Henwood. \emph{European Economic Sociology Newsletter} 6 (3):~37--38.

\ind  Kieran Healy. 2004. ``The Abundance of the Heart.'' Review of \emph{A Man After His Own Heart} by Charles
Siebert. \emph{Australian Review of Public Affairs}, October. Reprinted in the
\emph{Australian Financial Review}, October 22nd.

\ind  Kieran Healy. 2003. \href{http://links.jstor.org/sici?sici=0094-3061%28200303%2932%3A2%3C252%3AAEATOC%3E2.0.CO%3B2-F}{Review} of \emph{Against Essentialism} by Stephan Fuchs.
\emph{Contemporary Sociology} 32:~252--254.

\ind  Kieran Healy. 2001. Review of \emph{Market Society} by Don Slater and Fran Tonkiss. \emph{European
      Economic Sociology Newsletter} 3 (1):~31--32.


\ind  Kieran Healy. 1999. \href{http://links.jstor.org/sici?sici=0094-3061%28199903%2928%3A2%3C210%3ACPRCAS%3E2.0.CO%3B2-C}{Review} of \emph{Comparative Politics} by Mark Irving Lichbach and Alan S.
Zuckerman. \emph{Contemporary Sociology} 28:~210--211.


\ind  Kieran Healy. 1998. \href{http://www.kieranhealy.org/files/reviews/rule.pdf}{Review} of \emph{Theory and Progress in Social Science} by James Rule.  \emph{Theory
  and Society}, 27:~435--441.

% %\end{revnumerate}
 \bigskip

%% Presentations
\marginpar{\textsf{{\footnotesize\vspace{-0.6em}\flushright Invited Talks \newline (Since 2004)}}}
\medskip

\ind 2009. ``Specialization and Status in Philosophy.'' University of Chicago, Booth School of Business. May.

\ind 2009. ``Specialization and Status in Philosophy.'' University of California, Berkeley. April. 

\ind 2009. ``Specialization and Status in Philosophy.'' University of Michigan, \textsc{icos}. April.

\ind 2009. ``Specialization and Status in Philosophy.'' Columbia University. February. 

\ind 2009. ``The Performativity of Networks.'' Yale University. January.

\ind 2008. ``The Performativity of Networks.'' Stanford University Graduate School of Business. October. 

\ind 2008. ``The Performativity of Networks.'' Harvard/MIT Joint Seminar in Economic Sociology. March.

\ind 2007. ``Specialization and Status in Philosophy.'' University of Notre Dame. November. 

\ind 2007. ``Last Best Gifts: Altruism and the Market for Human Blood and Organs.'' Center for History, Society and Culure, University of California at Davis. November.

\ind 2007. ``Gift Fetishism and the Market for Human Organs.'' Department of Anthropology, University of Arizona. February. 

\ind 2007. ``Presumed Consent Law and Organ Procurement.'' Rogers Program on Law and Society, University of Arizona. January. 

\ind 2006. ``The Political Economy of Presumed Consent.'' Institute for Global
and International Studies, George Washington University. March.

\ind 2005. ``Last Best Gifts: Altruism and the Market for Human Organs.''
Columbia University School of Business. November. 

\ind 2005. ``The Political Economy of Presumed Consent.'' University of California, Los Angeles. May.

\ind 2005. ``Last Best Gifts: Altruism and the Market for Human Organs.''
University of California, Berkeley. April.

\ind 2005. ``Cadaveric Organ Procurement and Presumed Consent Laws.'' DePaul
Law Review \& Health Law Institute Symposium on \emph{Precious Commodities: The
Supply and Demand of Body Parts}. Chicago. March. 

\ind 2005. ``Last Best Gifts: Altruism and the Market for Human 
Organs.'' University of Washington. February. 

\ind 2004. ``The Institutional Context of Organ Procurement.'' Indiana
University--Purdue University, Indianapolis. November.

\ind 2004. ``The Political Economy of Presumed Consent.'' \textsc{spt} Program,
Australian National University, \textsc{rsss}. July. 

\ind 2004. ``Organ Procurement in the United States.'' National University of
Ireland at Maynooth. April. 

% \ind 2002. ``Creativity and the Creative Industries.'' Center for Arts and
% Culture, Washington DC. December.
% 
% \ind 2002. ``Altruism as an Organizational Problem: The case of organ
% procurement.'' Northwestern University.
% November.
% 
% \ind 2002. ``Sacred Markets and Secular Ritual in the Organ Transplant
% Industry.'' University of California at San Diego. November.
% 
% 
% \ind 2002. ``The Ecology of Open Source Software Development.'' Department of
% Sociology, University of Arizona. August.
% 
% \ind 2002. ``What's New for Culture in the New Economy?'' Sixth
% annual Summer Cultural Policy Meetings, New York. July.
% 
% 
% \ind 2002. ``Sacred Markets and Secular Ritual in the Organ Transplant Industry.''
%       Princeton Economic Sociology Conference, Princeton. February.
% 
% 
% \ind 2001. ``Altruism as a Resource-extraction Problem.'' Rational Choice 
% Section Miniconference, annual meetings of the American Sociological 
% Association, Anaheim. August.
% 
% 
% 
% \ind 2001. ``Culture and Technology.'' Keynote Address, Fifth Annual Summer Cultural
% Policy Meeting, Little Switzerland NC. June.
% 
% 
% 
% \ind 2000. ``Media Discourse on Organ Transplantation, 1980-2000.''  New York
% University Graduate Student Sociology Conference. March.
% 
% 
% 
% \ind 2000. ``Industrializing Altruism: The U.S. Organ Transplant Industry,
% 1978-1998.'' Princeton \textsc{joie} Workshop on Organizations, Institutions
% and Economic Sociology. March.
% 
% 
% 
% \ind 1999. Discussant, regular session on Democratic Transitions, annual
%   meetings of the American Sociological Association, Chicago. August.                     
%\end{revnumerate}

\bigskip

%\newpage

\marginpar{\textsf{{\footnotesize\vspace{-0.6em}\flushright Conference \newline Presentations \newline (Since 2004)}}}
\medskip

\ind 2008. Invited speaker, ASA Culture Section 20th Anniversary Symposium, ``Culture and Economy,'' Boston, August.

\ind 2008. Invited discussant, conference on Norms and Values, ZiF center, University of Bielefeld, Germany. May. 

\ind 2007. ``Economic Categories and the Claims of Neoliberal Society.'' Invited Session on Culture and Markets. Annual Meetings of the American Sociological Association, New York. August.

\ind 2007. ``The Performativity of Networks.'' Special Session on Money in Movement: Markets, Circuits and Networks. Annual Meetings of the American Sociological Association, New York. August.

\ind 2007. Presider, Regular Session on the Sociology of Knowledge. Annual Meetings of the American Sociological Association, New York. August.

\ind 2007. Discussant, Book Panel on Steven Levitt and Stephen Dubner's \emph{Freakonomics}. Annual Meetings of the Eastern Sociological Society, Philadelphia. March.

\ind 2006. ``The Political Economy of Presumed Consent.'' Annual Meetings of the American Sociological Association, Montreal. August.

\ind 2006. ``Specialization and Status in Philosophy.'' Annual Meetings of the American Sociological Association, Montreal. August.

\ind 2006. Discussant, Invited Session on Public Sociology. Annual Meetings of the American Sociological Association, Montreal. August.

\ind 2004. Discussant, Regular Session on the Political Economy of the World System. Annual Meetings of the American Sociological Association, San Francisco. August.

%\begin{revnumerate} \ind 2003. Discussant, Regular Session on Internet and Culture. Annual Meetings of the American Sociological Association, Atlanta. August.

% \ind 2003. ``The Ecology of Open Source Software.'' Annual Meetings of the American Sociological Association, Atlanta. August.



% \ind 2002. ``Altruism as an Organizational Problem: The case of organ
% procurement.'' Annual meetings of the American Sociological Association,
% Chicago. August.
% 
% 
% 
% \ind 2001. ``Cultural Accounts of Organ Donation.'' Annual meetings of the
% Eastern Sociological Society, Philadelphia. March.
%   
% 
% 
%   \ind 1998. ``Three Ways to Tap a Vein: Blood Collection Regimes and the
%   European Union's Donor Population.''  Annual meetings of the American
%   Sociological Association, San Francisco, August. 
% 
%   \ind 1997. ``Three Ways to Tap a Vein: Blood Collection Regimes and the European
%   Union's Donor Population.''  Princeton--Rutgers Conference on the Sociology
%   of Culture.
%   
% \ind 1998. ``Explaining the \textsc{oecd} Wage Slowdown: Recession or
% Labor Decline?''  With Bruce Western. Annual meetings of the American
% Sociological Association, San Francisco. August.
% 
% 
% 
% \ind 1997. ``Wage Growth and Labor Decline in the Advanced Capitalist
%   Countries, 1965--1993.'' With Bruce Western. Presented at ``Unemployment's
%   Effects: the Southern European Experience in Comparative Perspective,''
%   Southern European Research Group conference held at Princeton University,
%   November.
% 
% 
% 
% \ind 1997. ``The Organization of Obligation: Markets, Risk and the Blood
%   Supply.'' Annual meetings of the Eastern Sociological Assocation, Baltimore.
%   April.
% 
% % \medskip
% 
% % 1994. \emph{The Language of Influence: Public Debate and the Poliøtics of
% %     the X--Case}. M.A. Thesis, University College Cork, Ireland, October.
% 
% 
% 
% \ind 1994. ``Looking After Your Own: Youth Defence and Abortion.'' Annual
%   Meetings of the Irish Sociological Association, Derry. March.               
%\end{revnumerate}
% \newpage

\bigskip

\marginpar{\textsf{{\footnotesize\vspace{-0.6em}\flushright Grants and \newline Awards}}}
\medskip
  
\ind 2008. Honorable Mention, American Sociological Association Section on Economic Sociology, Zelizer Distinguished Scholarship Award.

\ind 2008-09. Residential Fellowship, Center for Advanced Study in the Behavioral Sciences, Stanford University.

\ind 2007. Winner, Association for Research on Nonprofit Organizations and Voluntary Action (\textsc{arnova}) Outstanding Book Prize.

\ind 2007. Finalist, Society for the Study of Social Problems (\textsc{sssp}), C. Wright Mills Award.

\ind 2006. Rogers Program in Law and Society, Faculty Research Award
(\$3,000), University of Arizona.

\ind 2006. Participant, Summer Institute on \emph{Economy and Society: Trajectories of Capitalism}, Center for Advanced Study in the Behavioral Sciences (July--August).

\ind 2003. University of Arizona \textsc{sbsri}/Center for Applied Spatial
Analysis. Geographical Information Systems Research Assistance
Program Award. ``The Geography of Organ Procurement.''

\ind 2002. American Sociological Association Dissertation Award.

\ind 2002. University of Arizona Prop.\,301 Information Technology/Information Science Fund. ``Understanding Open-Source Software Development: Network organizations, innovation and volunteering'' (\$19,500).

\ind 2000. National Science Foundation Doctoral Dissertation Research Improvement Award (\$7,500).

\ind 1998--2000. Graduate Fellow, Fellowship of Woodrow Wilson Scholars. Prize fellowship.

\ind 1998--1999. Noah Cotsen Junior Teaching Fellowship, Princeton University. Prize fellowship.

\ind 1998. Prize Paper, Princeton University Department of Sociology Working Paper Series.

\ind 1998. General Examinations with Distinction, Princeton University.

\ind 1995--1998. Graduate Fellowship, Princeton University.

\ind 1993--1994. Title of College Scholar, University College, Cork.

\ind 1991--1993. College Undergraduate Scholarship, University
College, Cork.

% \bigskip

% \noindent\hrulefill

% \noindent\textsf{{Courses Taught}}

% \ind Sociology of Culture. Graduate seminar. (Fall 2004.)

% \ind Economic Sociology. Graduate seminar. (Fall 2002.)

% \ind Sources of Sociological Theory. Upper-level undergraduate course. (Fall
% 2001, Twice; Spring 2002, Twice; Fall 2002; Fall 2004; Fall 2005, Twice.)

\bigskip 

\newpage

\marginpar{\textsf{{\footnotesize\flushright Service to the \newline Profession}}}
\medskip

\medskip

\ind Consulting Editor (2009--11), \emph{American Journal of Sociology}.

\ind Editorial Board Member (2008--10), \emph{Contexts}. 

\ind Prize Committee, American Sociological Association Section on Economic Sociology, Ronald Burt Prize Paper Award (2007--08).

\ind Elected Council Member, American Sociological Association Section on Economic
Sociology (2008--2010). 

\ind Co-ordinator of the Society for the Advancement of Socio-Economics' research network on Socio-Economic Theory (2006--2008). 

\ind Editorial Board Member (2007--2009), \emph{Socio-Economic Review}.

\ind Session organizer, Regular Session on Voluntary and Non-Profit organizations, American Sociological Association Meetings, Philadelphia, August 2005.

\ind Co-Editor (with Alexandra Kalev), \emph{Accounts}, Newsletter of the American Sociological Association Section on Economic Sociology (2003--2004 and 2004--2005).

\ind Prize committee, American Sociological Association Theory Section, Graduate Student Paper Award (2003--2004).

\ind Reviewer, National Science Foundation, \emph{American
  Sociological Review}, \emph{American Journal of Sociology},
\emph{American Journal of Transplantation}, \emph{Administrative
  Science Quarterly}, \emph{Bioethics}, \emph{Contexts}, \emph{The Information
  Society}, \emph{Journal of Health Economics}, \emph{Journal of Political Philosophy}, \emph{Journal for the Scientific Study of Religion}, \emph{Social Networks}, \emph{Socio-Economic Review}, \emph{Sociological Forum}, \emph{Transactions of the Institute of British Geographers}, \emph{Social Science \& Medicine}, \emph{Theory and Society}, Cambridge University Press, University of Chicago Press, Duke University Press, Oxford University Press, Polity Press, Sage Publications/Pine Forge Press.

\end{document}
